% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{letterpaper, margin=0.75in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{hyperref} % For hyperlinks
\usepackage{tabularx}
\usepackage{fancyhdr}

% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing
%%%%%%%%%%

% Begin document
\begin{document}

% Disable page numbers
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\fancyhead[L]{\textit{Clark Miyamoto}}
\thispagestyle{empty} % Remove header from the first page

% Header
\begin{flushleft}
\textbf{\LARGE Clark Miyamoto}\\[2pt] % Name
PhD Student, NYU Physics | New York, United States.
\\ \href{mailto:cm6627@nyu.edu}{cm6627@nyu.edu} | \href{https://www.linkedin.com/in/clarkmiyamoto}{linkedin.com/in/clarkmiyamoto} | \href{https://github.com/clarkmiyamoto}{GitHub/clarkmiyamoto} % Contact info
\end{flushleft}

% Education Section
\section*{Education}
\noindent
\textbf{New York University} \hfill 2023 | Current\\
Doctor of Philosophy, Physics  \hfill GPA: 3.97/4.00 \\ % Degree and GPA
\emph{Honors:} MacCracken Fellowship

\noindent\\
\textbf{University of Southern California} \hfill 2019 |  2023\\
Bachelor of Science, Physics \\
\emph{Honors:} Discovery Scholar, Magna Cum Laude, Physics Department Undergraduate Representative

% Experience Section
\section*{Research Experience}
\noindent
\textbf{New York University,} \textit{Graduate Research Assistant} \hfill 2023 | Current\\
Developed statistical inference methods under Prof. David Hogg.
\begin{itemize}
    \item Developed theory on hyperparameter tuning for affine invariant Hamiltonian Monte Carlo (HMC) methods.
    \item Implemented novel HMC method into pythonic open-source library.
    \item Developed theory on how Convolutional Neural Networks learned additional symmetries from training data, in collaboration with Soledad Villar.
    \item Ran computational experiments on JAX \& PyTorch on High Performance Computing cluster.
\end{itemize}

\noindent
Research rotations:
\begin{itemize}
    \item Dries Sels: Used Haar measure techniques to inspect expressivity of wavefunction ansatzs in the context of neural quantum states.
    \item Daniel Stein: Developed spin glass inspired theory of how beliefs propagate between humans in sociological systems. Collaborated with psychologist Prof. Mirta Galesic \& cognitive scientist Prof. Henrik Olsson.
\end{itemize}

\noindent
\textbf{University of Southern California,} \textit{Undergraduate Research Assistant} \hfill 2021 | 2023\\
Design and simulate superconducting quantum devices under Prof. Eli Levenson-Falk.
\begin{itemize}
    \item Created a pythonic open-source library to expedite the design \& simulation of quantum devices, reducing turnaround time from 40 to 4 hours. 
    \item Designed novel superconducting qubit devices which were part of published work.
    \item Built and optimized radio frequency mixing system, DAC, and power supply for superconducting qubit control systems.
\end{itemize}


\section*{Publications}
\begin{enumerate}
    \item (In preparation) \textbf{Clark Miyamoto}, Yifan Chen, 2025, \emph{Hyperparameter tuning for affine invariant Hamiltonian Monte Carlo}.
    \item (In preparation) \textbf{Clark Miyamoto}, Yifan Chen, David Hogg, 2025, \emph{h-emcee: pythonic affine invariant Hamiltonian Monte Carlo}.
    
    \item Vivek Maurya, Haimeng Zhang, Daria Kowsari, Andre Kuo, Darian M Hartsell, \textbf{Clark Miyamoto}, et al., 2024, \emph{On-demand driven dissipation for cavity reset and cooling}, PRX Quantum, \textbf{5}, 020321. 
 
    \item Sadman Shanto, Andre Kuo, \textbf{Clark Miyamoto}, et al., 2024, \emph{SQuADDS: A validated design database and simulation workflow for superconducting qubit design}, Quantum, \textbf{8}, 1465.
\end{enumerate}

\section*{Conferences / Workshops}
\begin{itemize}
    \item Princeton Machine Learning Theory Summer School \hfill 2025\\
    \noindent Poster: \emph{Hyperparameter tuning for affine invariant Hamiltonian Monte Carlo.}
    \item IAIFI Summer School \hfill 2025
    \item Beg Rohu Summer School of Physics: Learning with Machines, Physics and Minds. \hfill 2025\\
    \noindent Poster: \emph{How CNNs learn additional symmetries.}
    \item American Physics Society, March Meeting. \hfill 2023\\
    Poster: \emph{Developing a library of modular superconducting qubit components for rapid device design.}
\end{itemize}

\newpage
\section*{Selected Courses}
\begin{itemize}
    \item Data Science for Physicists
    \item Machine Learning for Physicists
    \item Inference and Representation (Audited)
    \item Bayesian Machine Learning (Audited)
    \item Stochastic Calculus (Audited) 
    \item Stochastic Optimal Control for Finance (Audited)
    \item Statistical Physics
    \item Quantum Field Theory I \& II
\end{itemize}

\section*{Teaching}
\textbf{Teaching Assistant} at New York University
\begin{itemize}
	\item PHYS-UA 131: Electricity \& Magnetism I \hfill Fall 2025
    \item PHYS-UA 91: Physics I for Majors \hfill Fall 2024
\end{itemize}

\section*{Volunteer Experience}

\textbf{New York University}, Seminar Organizer \hfill 2023 | Current
\begin{itemize}
    \item Organize a weekly seminar on generative models in the math \& data science departments.
    \item Initated a weekly machine learning seminar in the physics department.
\end{itemize}

\noindent
\textbf{University of Southern California}, Physics Department Undergraduate Representative \hfill 2022 | 2023
\begin{itemize}
    \item Designed and implemented a new physics course: PHYS 499 String Theory for Undergrads.
    \item Updated introductory physics course curriculum to include Python coding.
    \item Host various professional and social events to help undergrads find a sense of community within the department. 
\end{itemize}

\end{document}
